---
title: 'H1: Correlation_between_appearance_involvement_and_physical_distress_analysis'
output: html_document
date: "2026-04-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

d_rednote <- read.csv('../data/RedNote_Survey.csv')
```


# Calculate descriptive statistics for key variables
```{r}
d_rednote %>%
  summarise(
    # Statistics on the frequency of appearance-related activities
    Appearance_Activity_M = round(mean(Appearance_Activity_Total), 2),
    Appearance_Activity_SD = round(sd(Appearance_Activity_Total), 2),
    Appearance_Activity_Mdn = round(median(Appearance_Activity_Total), 2),
    Appearance_Activity_Range = paste(min(Appearance_Activity_Total), "-", max(Appearance_Activity_Total)),
    
    # Statistics on the degree of body intention distress
    BSQ8A_M = round(mean(BSQ8A_Total), 2),
    BSQ8A_SD = round(sd(BSQ8A_Total), 2),
    BSQ8A_Mdn = round(median(BSQ8A_Total), 2),
    BSQ8A_Range = paste(min(BSQ8A_Total), "-", max(BSQ8A_Total))
  )
```

# Calculate correlation
```{r}
# Calculate the Pearson correlation coefficient
correlation_result <- cor.test(
  d_rednote$Appearance_Activity_Total,
  d_rednote$BSQ8A_Total,
  method = "pearson",
  conf.level = 0.95
)

# Output correlation analysis results
print(correlation_result)

# Extract correlation coefficient and p-value
r_value <- round(correlation_result$estimate, 3)
p_value <- round(correlation_result$p.value, 3)
conf_int <- round(correlation_result$conf.int, 3)

```


# Draw a scatter plot
```{r}
ggplot(d_rednote, aes(x = Appearance_Activity_Total, y = BSQ8A_Total)) +

  geom_point(alpha = 0.6, size = 3, color = "#E1306C") +
  
  geom_smooth(method = "lm", se = TRUE, color = "#1DA1F2", linewidth = 1.2) +
 
  labs(
    title = "The Relationship Between the Frequency of Appearance-Related Activities on Xiaohongshu and the Level of Body Affectiveness",
    subtitle = paste0("Pearson correlation coefficient r = ", r_value, ", p = ", p_value),
    x = "Total score for frequency of participation in appearance-related activities",
    y = "Total score of body intention distress(BSQ-8A)",
  ) +
  
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 10)
  ) +
  
  theme(panel.grid = element_line(alpha = 0.3))
```


# Findings

The analysis of Pearson’s product-moment correlation revealed a **strong positive association** between users’ frequency of engaging in appearance-related activities on Xiaohongshu and their level of body image disturbance (BSQ-8A score).  

Specifically, there was a statistically significant correlation between the two variables, *r*(99) = .60, *p* < .001, with the 95% confidence interval for the correlation coefficient ranging from .46 to .71. The magnitude of the correlation indicates a moderate-to-strong linear relationship: higher engagement in appearance-related activities (such as editing photos, posting selfies, and viewing beauty/fitness content) was associated with greater body image disturbance.  

This finding provides **strong support for Hypothesis 1**, as the data confirms the predicted positive association between appearance-related activity frequency and body image distress.
