---
title: "H2- Anxiety_Group_BodyDistress_Comparison"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

d_rednote <- read.csv('../data/RedNote_Survey.csv')
```


# Hypothesis 2
Users with high anxiety levels experienced significantly higher levels of body ideological distress after browsing Xiaohongshu compared to users with low anxiety levels.

```{r}
d_rednote <- d_rednote %>%
  mutate(Anxiety_Group = ifelse(GAD7_Total <= 9, "Low_Anxiety", "High_Anxiety"))
```

```{r}
d_rednote %>%
  group_by(Anxiety_Group) %>%
  summarise(
    n = n(),
    M = mean(BSQ8A_Total),
    SD = sd(BSQ8A_Total)
  )
```

```{r}
t.test(
  BSQ8A_Total ~ Anxiety_Group,
  data = d_rednote
)
```


# Findings

High anxiety users showed significantly higher body image disturbance than low anxiety users. Specifically, the high anxiety group (M = 28.78, SD = 10.37) reported greater body image distress than the low anxiety group (M = 20.83, SD = 10.12), Welch’s t(52.96) = 3.55, p = .001. The 95% confidence interval for the mean difference ranged from 3.45 to 12.45.

This finding supports Hypothesis 2.
