---
title: "H3- BodyConcern_FitnessBrowsing_Association"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

d_rednote <- read.csv('../data/RedNote_Survey.csv')
```

# Hypothesis 3
Users with high body image concerns are more likely to browse appearance-related content (weight loss/fitness).

```{r}
d_rednote <- d_rednote %>%
  mutate(
    Body_Image_Group = ifelse(BSQ8A_Total >= 26, "High_Distress", "Low_Distress"),
    Content_Preference = ifelse(Appearance_Content_Score > median(Appearance_Content_Score), "Appearance_Focused", "Neutral")
  )
```

```{r}
table(d_rednote$Body_Image_Group, d_rednote$Content_Preference)
```

```{r}
chisq.test(
  d_rednote$Body_Image_Group,
  d_rednote$Content_Preference
)
```


# Findings

A chi-square test revealed a significant association between body image distress group and content preference on RedNote, χ²(1, N = 101) = 9.31, p = .002.

Users with high body image distress were more likely to prefer appearance-focused content, whereas users with low body image distress were more likely to prefer neutral content.

This result supports Hypothesis 3.
